### 2021-11-07 paper/output/document/paper22.tex
finished application tests for Kroy - next steps are to port learnings to the naive interpretation, and move on to metaethical tests
added maxim
cleaned much of naive

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{2}}{\isadigit{2}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Isabelle/HOL Implementation \label{sec:isabelle}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Isabelle/HOL is an interactive proof assistant \cite{isabelle} built on Haskell and Scala. It 
allows the user to define types, functions, definitions, and axiom systems. It has built-in support for both
automatic and interactive/manual theorem proving.

I started my project by reimplementing Benzmueller, Farjami, and Parent's \cite{BFP, logikey} implementation 
of DDL in Isabelle/HOL. This helped me learn how to use Isabelle/HOL, and the implementation showcased in the 
next few sections demonstrates the power of Isabelle.

BFP use a shallow semantic embedding. This kind of embedding models the semantics of DDL as 

@@

the accessibility relations. These axioms can be quite unweildy, so luckily I was able to lift BFP's \cite{BFP}
implementation of Carmo and Jones's original axioms directly. Here's an example of an axiom:%

@@

@@

world. BFP \cite{BFP} provide a complete treatment of the completeness of their embedding, but I 

@@

  Empty assignment \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Nitpick \cite{nitpick} can generate models or countermodels, so it's useful to falsify potential
theorems, as well as to show consistency. {\color{red} by simp} indicates the proof method. In this 
case, {\color{red} simp} indicates the Simplification proof method, which involves unfolding definitions
and applying theorems directly. HOL has $True$ as a theorem, which is why this theorem was so easy to prove.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper22.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%56=22%:%
%:%68=24%:%
%:%70=26%:%
%:%71=26%:%
%:%72=26%:%
%:%73=26%:%
%:%74=27%:%
%:%75=28%:%
%:%76=28%:%
%:%77=28%:%
%:%78=28%:%
%:%80=29%:%
%:%81=30%:%
%:%82=30%:%
%:%85=44%:%
%:%87=46%:%
%:%88=46%:%
%:%89=46%:%
%:%90=46%:%
%:%91=47%:%
%:%92=47%:%
%:%93=47%:%
%:%101=51%:%
%:%113=53%:%
%:%114=54%:%
%:%115=55%:%
%:%116=56%:%
%:%118=80%:%
%:%119=81%:%
%:%120=82%:%
%:%122=83%:%
%:%123=84%:%
%:%124=85%:%
%:%125=86%:%
%:%126=86%:%
%:%134=93%:%
%:%146=95%:%
%:%147=96%:%
%:%148=97%:%
%:%149=98%:%
%:%150=99%:%
%:%151=100%:%
%:%155=116%:%
%:%157=117%:%
%:%158=117%:%
%:%159=118%:%
%:%160=119%:%
%:%161=119%:%
%:%162=120%:%
%:%164=122%:%
%:%166=123%:%
%:%167=123%:%
%:%168=124%:%
%:%170=125%:%
%:%171=125%:%
%:%174=145%:%
%:%175=146%:%
%:%177=147%:%
%:%178=147%:%
%:%179=148%:%
%:%180=149%:%
%:%181=149%:%
%:%182=150%:%
%:%184=151%:%
%:%187=153%:%
%:%189=154%:%
%:%190=154%:%
%:%191=155%:%
%:%199=162%:%
%:%211=164%:%
%:%212=165%:%
%:%213=166%:%
%:%214=167%:%
%:%215=168%:%
%:%219=170%:%
%:%221=171%:%
%:%222=171%:%
%:%223=171%:%
%:%225=171%:%
%:%229=171%:%
%:%230=171%:%
%:%232=172%:%
%:%233=173%:%
%:%234=173%:%
%:%236=174%:%
%:%237=175%:%
%:%238=176%:%
%:%248=178%:%
%:%249=179%:%
%:%250=180%:%
%:%251=181%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{2}}{\isadigit{2}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Isabelle/HOL Implementation \label{sec:isabelle}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The final component of my project is the automated theorem prover I use to automate my formalization.
Isabelle/HOL is an interactive proof assistant built on Haskell and Scala \cite{isabelle}. It 
allows the user to define types, functions, definitions, and axiom systems. It has built-in support for both
automatic and interactive/manual theorem proving.

I started my project by reimplementing Benzmueller, Farjami, and Parent's implementation 
of DDL in Isabelle/HOL \cite{BFP, logikey}. This helped me learn how to use Isabelle/HOL, and the implementation showcased in the 
next few sections demonstrates the power of Isabelle.

Benzmueller, Farjami, and Parent use a shallow semantic embedding. This kind of embedding models the semantics of DDL as 

@@

the accessibility relations. These axioms can be quite unweildy, so luckily I was able to lift BFP's 
implementation of Carmo and Jones's original axioms directly \citep{BFP}. Here's an example of an axiom:%

@@

\ ddlfalse{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbottom}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbottom}\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ False{\isachardoublequoteclose}\isanewline

@@

world. Benzmueller, Farjami, and Parent provide a complete treatment of the completeness of their embedding, but I 

@@

  Empty assignment \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Nitpick \cite{nitpick} can generate models or countermodels, so it's useful to falsify potential
theorems, as well as to show consistency. {\color{red} by simp} indicates the proof method. In this 
case, {\color{red} simp} indicates the Simplification proof method, which involves unfolding definitions
and applying theorems directly. HOL has $True$ as a theorem, which is why this theorem was so easy to prove.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper22.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%48=20%:%
%:%57=23%:%
%:%69=25%:%
%:%71=27%:%
%:%72=27%:%
%:%73=27%:%
%:%74=27%:%
%:%75=28%:%
%:%76=29%:%
%:%77=29%:%
%:%78=29%:%
%:%79=29%:%
%:%81=30%:%
%:%82=31%:%
%:%83=31%:%
%:%86=45%:%
%:%88=47%:%
%:%89=47%:%
%:%90=47%:%
%:%91=47%:%
%:%92=48%:%
%:%93=48%:%
%:%94=48%:%
%:%102=52%:%
%:%114=54%:%
%:%115=55%:%
%:%116=56%:%
%:%117=57%:%
%:%119=81%:%
%:%120=82%:%
%:%121=83%:%
%:%123=84%:%
%:%124=85%:%
%:%125=86%:%
%:%126=87%:%
%:%127=87%:%
%:%135=94%:%
%:%147=96%:%
%:%148=97%:%
%:%149=98%:%
%:%150=99%:%
%:%151=100%:%
%:%152=101%:%
%:%156=117%:%
%:%158=118%:%
%:%159=118%:%
%:%160=119%:%
%:%161=120%:%
%:%162=120%:%
%:%163=121%:%
%:%165=123%:%
%:%167=124%:%
%:%168=124%:%
%:%169=125%:%
%:%171=126%:%
%:%172=126%:%
%:%175=146%:%
%:%176=147%:%
%:%178=148%:%
%:%179=148%:%
%:%180=149%:%
%:%181=150%:%
%:%182=150%:%
%:%183=151%:%
%:%184=152%:%
%:%185=152%:%
%:%186=153%:%
%:%188=154%:%
%:%191=156%:%
%:%193=157%:%
%:%194=157%:%
%:%195=158%:%
%:%203=167%:%
%:%215=169%:%
%:%216=170%:%
%:%217=171%:%
%:%218=172%:%
%:%219=173%:%
%:%223=175%:%
%:%225=176%:%
%:%226=176%:%
%:%227=176%:%
%:%229=176%:%
%:%233=176%:%
%:%234=176%:%
%:%236=177%:%
%:%237=178%:%
%:%238=178%:%
%:%240=179%:%
%:%241=180%:%
%:%242=181%:%
%:%252=183%:%
%:%253=184%:%
%:%254=185%:%
%:%255=186%:%
